Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-26 paper-ieee-trans.tex
fix typo in biblio

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{images/fig3.png}
\caption{Adoption of Configuration Management tools throughout the project lifetime. Also shown the trend lines
leading to the first release (dark blue points and lines), and to the second release (light cream points and lines).}
\label{fig:fig_confman}
\end{figure}

@@

\bibitem{ggus}
T. Antoni, et al.,
Global grid user support—building a worldwide distributed user support infrastructure,
\emph{J. Phys.: Conf. Ser.},
vol. 119, n. 5, 052002, 2008.

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{images/fig3.png}
\caption{Adoption of Configuration Management tools throughout the project lifetime. Also shown the trend lines
leading to the first release (light cream points and lines), and to the second release (dark blue points and lines).}
\label{fig:fig_confman}
\end{figure}

@@

\bibitem{ggus}
T. Antoni, et al.,
Global grid user support--building a worldwide distributed user support infrastructure,
\emph{J. Phys.: Conf. Ser.},
vol. 119, n. 5, 052002, 2008.
